### 2019-10-10 letter.tex
small changes to the letter, testing the overleaf github sync

\section*{Resubmission of the InfoVis 2019 submission titled ``Extending Spreadsheets to Support Seamless
Navigation at Scale'' to TVCG}

A previous version of this paper was submitted to InfoVis 2019. This version was rejected as the paper co-chairs deemed that revising the paper would require more time than allocated to meet reviewer expectations for the conference. The paper co-chairs mentioned the following: ``\textit{We particularly encourage such revisions where submissions were positively received by reviewers, but the revisions required were deemed to be beyond the scope of the conference review cycle. If you address the issues raised and subsequently submit to IEEE TVCG, please make reference to this IEEE InfoVis submission and include a description of how you addressed the InfoVis reviewers' comments.}''

The present version of the paper addresses all of the issues mentioned by the reviewers. The entire set of reviews are attached. In particular, the reviewers asked for the following changes for a revision: \begin{itemize}
    \item More clearly articulate the merits over alternative tools, such as Keshif. 
     \item Convincingly explain the design choice around the binning mechanism or revise
    that approach.
    \item Justify the choice of comparing with Excel and note the limitations of that
    approach.
     \item Better justify the choice of tasks in the study. 
     \item Explain the choice of the four research questions.
     \item Provide more details about the study, including reporting intra-participant
    differences.
\end{itemize}

Here, we provide a response to the reviews. In our revised submission,
\textbf{(i) we discuss the merits of introducing a spreadsheet integration like \noah over alternative tools, \eg Keshif;
(ii) we explain our design choice surrounding the binning mechanism;
and 
(iii) we enrich the user study design section further by providing justification for comparing \noah and Excel, rephrasing our research questions reflecting the purpose of the user study, explaining the choice of quiz tasks,
iv) we reorganize the results section to  highlight key contributions of \noah while explaining participant experiences in using the tool. Moreover, we report the  intra-participant differences for the study}. 
The major changes to the paper include:

>>>>

%!TEX root = main.tex

\section*{Resubmission of InfoVis 2019 submission ``Extending Spreadsheets to Support Seamless
Navigation at Scale'' to TVCG}

A previous version of this paper was submitted to InfoVis 2019. This version was rejected as the paper co-chairs deemed that revising the paper would require more time than allocated to meet reviewer expectations. The paper co-chairs mentioned the following: ``\textit{We particularly encourage such revisions where submissions were positively received by reviewers, but the revisions required were deemed to be beyond the scope of the conference review cycle. If you address the issues raised and subsequently submit to TVCG, please make reference to this  InfoVis submission and include a description of how you addressed the InfoVis reviewers' comments.}''

The present version of the paper addresses all of the issues mentioned by the reviewers. The entire set of reviews are attached. In particular, the reviewers asked for the following changes for a revision: 
\begin{itemize}
    \item More clearly articulate the merits over alternative tools, such as Keshif. 
     \item Convincingly explain the design choice around the binning mechanism or revise
    that approach.
    \item Justify the choice of comparing with Excel and note the limitations of that
    approach.
     \item Better justify the choice of tasks in the study. 
     \item Explain the choice of the four research questions.
     \item Provide more details about the study, including reporting intra-participant
    differences.
\end{itemize} 
We have spent the last four months 
preparing a revised version of this paper.
\agp{One thing that is confusing is that the bulletpoints above
don't neatly map to the bulletpoints below, or the enumerated list after that.}
Here, we provide a response to the reviews. 
In our revised submission,
(i) we discuss the merits of having an interface like \noah
integrated within an existing spreadsheet, as opposed
to other general-purpose exploratory tools such as  Keshif;
(ii) we justify our design choice surrounding the binning mechanism;
and 
(iii) we enrich the user study design section further 
by providing justifications for comparing \noah and Excel, 
rephrasing our research questions reflecting the purpose of the user study, explaining the choice of quiz tasks,
(iv) we reorganize the results section to  highlight key contributions of \noah while explaining participant experiences in using the tool. Moreover, we report the  intra-participant differences for the study. 
The major changes to the paper include:
